PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Changed dataset to read in combined CFS + baseline data

>>>>

# Demographics
## Ethnicity_collapsed
### Pie charts
**NEED TO CREATE ETHNICITY_collapsed variable**
```{r Ethnicity_collapsed prop per total summary}
Ethnicity_collapsed_prop_Covid <- dat.raw %>%
  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
  drop_na() %>%
  mutate(freq = round(n/sum(n), 2))

# total responders
ethN <- sum(Ethnicity_collapsed_prop_Covid$n)

kable(Ethnicity_collapsed_prop_Covid)
Ethnicity_collapsed_prop_Covid
```

pie chart with only European label

```{r ethnicity pie chart biggest group label}
eth_pie_alllabel <- 
  Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")  +
    geom_text(aes(y = c(0.5),
                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
             size=5,
             face="bold"
             )

eth_pie_alllabel
```

Pie chart - no labels

```{r ethnicity pie chart no label}
eth_pie_nolabel <- 
  Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")

eth_pie_nolabel
```
